An IFS study of Low-powered Radio Galaxies

### 2018-11-11 paper.tex
Minor alterations to paper
Remove OIII maps from PKS0718-34 and NGC1399 maps.

 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   produce_maps.py

	\subsection{Comparison to the Literature}
		\label{subsec:Lit}
		Given that there is no well defined list of corrections (and correction methods) that is universally followed, care must be taken when making comparisons to the literature. When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:absorption}. As in Section \ref{subsec:Mgsigma} we use a resolution of 8.4\,\AA\ FWHM in order to use the transformation function provided by \citet{Vazdekis2010} from Lick/IDS system to the LIS.

@@

		We also observe that the offset in the Fe5015 index is also quite large in comparisons with \citet{Rampazzo2005} and \citet{Vazdekis2010}. In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission doublet, however the origin of the offset is less clear in case of the comparison with \citet{Vazdekis2010}.

@@

\section{Stellar Populations}
	\label{sec:stellarPop}
	We have assumed that a given spectrum from our Southern sample can be well approximated by a SSP. We use the method described in Section \ref{subsubsec:stellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:maps}).

	In general, our sample galaxies show old, metal rich and alpha enhanced SSPs; qualities which ETGs are well known for. The exception is NGC 612 and NGC 1316. NGC 1316 shows a very young stellar population (our fit of $t \approx 2$\,Gyr agrees with that of \citealt{Kuntschner2000}, but is conflicting with the older and less metal rich stellar population of \citealt{Koleva2011} who found $t=4.5 \pm 0.3 \,\mathrm{Gyr}$ and $\mathrm{[Fe/H]}=0.12 \pm 0.01 \,\mathrm{dex}$ for an aperture covering the central 0.1 kpc). We also find NGC 612 to have a young stellar population of $t\approx 4\,\mathrm{Gyr}$. NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the south-east branch of the molecular gas (white contours in Fig \ref{fig:ngc3100}).

@@

	\subsection{Kinematically-Decoupled Cores}
		\label{subsec:popKDC}
		\citet{Kuntschner2010} found that KDCs can be separated two classes: they are either small with various stellar ages or typically larger but containing an old stellar population. The size of the KDC is defined as the radius of the region surrounding the KDC where the superposition of the two components (the KDC and the host galaxy) results in a local minimum in the mean velocity. The age of the most-likely SSP model for the spatially integrated spectrum within an aperture 1\arcsec\ on the centre of the galaxy is taken as the KDC's age.

		The small KDCs are too small to be spatially resolved by our data, and thus are not considered here. The larger, old KDCs are typically embedded in slow rotators. They have no upper limit on the age of their stellar populations suggesting that the stars within the KDC dominate in total mass as well as surface brightness. Thus, they do not fade into their host galaxies as they age unlike the small KDCs \citep{Kuntschner2010}. \citet{Bois2011} showed major mergers may well result in such large KDCs if the initial spin axis of the progenitor galaxy with the lowest bulge-to-disc ratio (later-type) is anti-parallel to the orbital angular momentum vector.

		In Fig.\,\ref{fig:KDC} we show the age and size of the 3 KDCs hosted by galaxies in our Southern sample. We include PKS 718-34 here but stress it is only tentatively classified as containing a KDC. As can be seen from Fig.\,\ref{fig:KDC}, PKS 718-34 would be an extremely large KDC, but is still consistent with the findings of \citet{Kuntschner2010}.

@@

\section{Ionized Gas Distribution, Kinematics and Ionization}
	\label{sec:gas}
	Using the methods described in Section \ref{subsubsec:EmissionFit}, we find the best-fitting line-of-sight velocity distribution (LOSVD; assumed to be Gaussian and parametrised by the mean velocity and velocity dispersion only) of the emission lines in each bin. Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet are shown in Appendix \ref{sec:maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first, see Section \ref{subsubsec:EmissionFit}).

	Only 4 galaxies of the Southern Sample have emission lines detected outside of their central region (IC 1459, NGC 612, NGC 1316 and NGC 3100). Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detection of H$\beta$ in their spatially-resolved map (although we do detect H$\beta$ in the spatially-integrated spectrum of NGC 1399; see Table \ref{tab:derivedProp}), while the other 5 galaxies are only detected in their centre. All other emission lines have similar distributions, but with different fluxes.

>>>>

	\subsection{Comparison to the Literature}
		\label{subsec:Lit}
		Given that there is no well defined list of corrections (and correction methods) that is universally followed, care must be taken when making comparisons to the literature. When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:absorption}. As in Section \ref{subsec:Mgsigma} we use a resolution of 8.4\,\AA\ FWHM in order to act on the literature values with the transformation function provided by \citet{Vazdekis2010} to provide a fair comparison between indices.

@@

		We also observe that the offset in the Fe5015 index is also quite large in comparisons with \citet{Rampazzo2005} and \citet{Vazdekis2010}. In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission doublet, however the origin of the offset is less clear when comparing to \citet{Vazdekis2010}.

@@

\section{Stellar Populations}
	\label{sec:stellarPop}
	Assuming that a given spectrum from our Southern sample can be well approximated by a SSP, we use the method described in Section \ref{subsubsec:stellarPop} to produce maps of the most-likely SSP characteristics: age ($t$), metallicity ($Z/H$) and alpha-element enhancement ($\alpha$/Fe) from the absorption line strength maps (see Appendix \ref{sec:maps}).

	In general, the Southern sample show old, metal rich and alpha enhanced SSPs; qualities which ETGs are well known for. The exceptions are NGC 612 and NGC 1316. NGC 1316 shows a very young stellar population (our fit of $t \approx 2$\,Gyr agrees with that of \citealt{Kuntschner2000}, but is conflicting with the older and less metal rich stellar population of \citealt{Koleva2011} who found $t=4.5 \pm 0.3 \,\mathrm{Gyr}$ and $\mathrm{[Fe/H]}=0.12 \pm 0.01 \,\mathrm{dex}$ for an aperture covering the central 0.1 kpc). We also find NGC 612 to have a young stellar population of $t\approx 4\,\mathrm{Gyr}$. NGC 3557 is notable for containing a significantly younger ($t\approx 4$\,Gyr) core of about 10\arcsec\ diameter and NGC 3100 has a branch of young stars ($\approx 4$\,Gyr) along the south-east branch of the molecular gas (white contours in Fig.\,\ref{fig:ngc3100}).

@@

	\subsection{Kinematically-Decoupled Cores}
		\label{subsec:popKDC}
		\citet{Kuntschner2010} showed that KDCs can be separated two classes: they are either small with various stellar ages or typically larger but containing an old stellar population. The size of the KDC is defined as the radius of the region surrounding the KDC where the superposition of the two components (the KDC and the host galaxy) results in a local minimum in the mean velocity. The age of the most-likely SSP model for the spatially integrated spectrum within an aperture 1\arcsec\ on the centre of the galaxy is taken as the KDC's age.

		The typical size of the smaller class of KDCs are too small to be spatially resolved by our data and thus are not considered here. The generally larger, old KDCs are typically embedded in slow rotators \citep{Kuntschner2010}. They have no upper limit on the age of their stellar populations suggesting that the stars within the KDC dominate in total mass as well as surface brightness, since they do not fade into their host galaxies as they age unlike the small KDCs \citep{Kuntschner2010}. \citet{Bois2011} showed major mergers may well result in such large KDCs if the initial spin axis of the progenitor galaxy with the lowest bulge-to-disc ratio (later-type) is anti-parallel to the orbital angular momentum vector.

		In Fig.\,\ref{fig:KDC} we show the age and size of the 3 KDCs hosted by galaxies in our Southern sample. We include PKS 718-34 here but we stress it is only tentatively classified as containing a KDC. As can be seen from Fig.\,\ref{fig:KDC}, PKS 718-34 would be an extremely large KDC, but all three are still consistent with the findings of \citet{Kuntschner2010}.

@@

\section{Ionized Gas Distribution, Kinematics and Ionization}
	\label{sec:gas}
	Using the methods described in Section \ref{subsubsec:EmissionFit}, we find the best-fitting LOSVD of the emission lines in each bin . As with the stellar LOSVD, this is assumed to be Gaussian in shape and parametrised by the mean velocity and velocity dispersion only. Images of the Southern Sample galaxies in the [\ion{O}{iii}]$\lambda\lambda$4957,5007 doublet are shown in Appendix \ref{sec:maps} (we choose to show [\ion{O}{iii}] as detections of all emission lines require a detection of [\ion{O}{iii}] first; see Section \ref{subsubsec:EmissionFit}).

	Only 4 galaxies of the Southern Sample have emission lines detected outside of their central region (IC 1459, NGC 612, NGC 1316 and NGC 3100). Of the remaining 7 galaxies, NGC 1399 and PKS 718-34 have no detections of emission lines in their spatially-resolved map (which are therefore not shown), while the other 5 galaxies are only detected in their centre. For a given galaxy, all emission lines have similar distributions, but different fluxes.
